Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-24 writing/CONUS_AOD.qmd
Support Word output with `flextable`.

format: 
  html:
    embed-resources: true

echo: FALSE
df-print: kable
---

```{r basics}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
     source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
   {library(patchwork)
    library(ggridges)
    library(kableExtra)
  })
the.sat = tools::toTitleCase(Wf$satellite)
IG = knitr::include_graphics
```

@@

```{r describe_dv}
kable(summary(dt[, list(y.diff)]))
```

@@

```{r table_cv_results}
kbl(pretty.table.numbers(tar_read(cv.summary)[1, -"Year"]), align = "l", caption = "Table ##. Cross validation results for the entire training set") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:12, width = "1.1cm")
```

@@

```{r strata_noaa_regions, fig.pos="H"}
# performance by NOAA climate regions
by.region = (dt
    [, eval(performance.j), by = state.noaa.region]
    [order(`Proportion of raw MSE`)])
kbl(pretty.table.numbers(by.region),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

@@

```{r strata_month}
result <- dt[,
    keyby = .(Month = month(lubridate::as_datetime(time.sat))),
    eval(performance.j)]
result[, Month := month.abb[Month]]
kbl(pretty.table.numbers(result), align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

```{r strata_high_aod, fig.pos="H"}
by.highaod = dt[, eval(performance.j), by = .(aod_high = y.ground > 0.6)]
kbl(pretty.table.numbers(by.highaod),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

@@

```{r strata_qa}
by.qabest = dt[, eval(performance.j), by = qa_best]
kbl(pretty.table.numbers(by.qabest),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

```{r shap_rank}
# what do the SHAPs tell us?
tar_load(cv)
shaps <- cv$"shap_score"
# sort by importance
df_shap <- data.frame(meanabsshap = round(sort(sapply(abs(shaps), mean), decreasing = TRUE), 4))
kbl(df_shap, col.names = "Mean |SHAP|") %>% row_spec(0, bold=TRUE)
# df_shap$variable <- row.names(df_shap)
# ft_shap <- flextable(df_shap[, c(2, 1)])
# ft_shap <- set_header_labels(ft_shap, list(variable = "Variable", meanabsshap = "Mean Absolute SHAP"))
# ft_shap
```

@@

```{r strata_year}
kbl(pretty.table.numbers(tar_read(cv.summary)[-1]),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(1:13, width = "1.1cm")
```

@@

```{r strata_overpasses, fig.pos="H"}
dt[, overpasses := .N, by = .(site, lubridate::as_date(time.ground))]
by.overpasses = dt[, eval(performance.j), keyby = overpasses]
kbl(pretty.table.numbers(by.overpasses),
    align = "l") %>%
  kable_styling(position = "left",
                latex_options=c("HOLD_position","scale_down")) %>%
  row_spec(0,bold=TRUE) %>% column_spec(2:13, width = "1.1cm")
```

>>>>

format:
  html:
    embed-resources: true
  docx: {}

echo: FALSE
---

```{r basics}
source.files = "globals libraries util data modeling paper_functions"
for (filename in strsplit(source.files, " ")[[1]])
     source(sprintf("code/%s.R", filename))
suppressPackageStartupMessages(
   {library(patchwork)
    library(ggridges)
    library(flextable)
  })
the.sat = tools::toTitleCase(Wf$satellite)
IG = knitr::include_graphics
```

@@

```{r describe_dv}
summary(dt[, list(y.diff)])
```

@@

```{r}
flextable(pretty.table.numbers(tar_read(cv.summary)[1, -"Year"]))
```

@@

```{r}
# performance by NOAA climate regions
by.region = (dt
    [, eval(performance.j), by = state.noaa.region]
    [order(`Proportion of raw MSE`)])
flextable(pretty.table.numbers(by.region))
```

@@

```{r}
result <- dt[,
    keyby = .(Month = month(lubridate::as_datetime(time.sat))),
    eval(performance.j)]
result[, Month := month.abb[Month]]
flextable(pretty.table.numbers(result))
```

@@

```{r}
by.highaod = dt[, eval(performance.j), by = .(aod_high = y.ground > 0.6)]
flextable(pretty.table.numbers(by.highaod))
```

@@

```{r}
by.qabest = dt[, eval(performance.j), by = qa_best]
flextable(pretty.table.numbers(by.qabest))
```

@@

```{r}
# what do the SHAPs tell us?
tar_load(cv)
shaps <- cv$"shap_score"
# sort by importance
df_shap <- data.frame(meanabsshap = round(sort(sapply(abs(shaps), mean), decreasing = TRUE), 4))
flextable(df_shap)
# df_shap$variable <- row.names(df_shap)
# ft_shap <- flextable(df_shap[, c(2, 1)])
# ft_shap <- set_header_labels(ft_shap, list(variable = "Variable", meanabsshap = "Mean Absolute SHAP"))
# ft_shap
```

@@

```{r}
flextable(pretty.table.numbers(tar_read(cv.summary)[-1]))
```

@@

```{r}
dt[, overpasses := .N, by = .(site, lubridate::as_date(time.ground))]
by.overpasses = dt[, eval(performance.j), keyby = overpasses]
flextable(pretty.table.numbers(by.overpasses))
```
